Tomographic galaxy clustering with the Subaru Hyper Suprime-Cam first year public data release

### 2019-10-20 doc/Paper/main.tex
Went through intro and conclusions.

In studies of the low redshift universe, surveys of the large scale structure play an increasingly important role. Over a decade ago, the Dark Energy Task Force has divided the evolution of optical experiments into approximate stages \cite{0609591}. The current Stage III experiments, including spectroscopic surveys such as eBOSS \cite{1707.09322,1801.03038,1712.08064,1801.02689,1801.02891} and VIPERS \cite{1611.07048,1612.05645,1708.00026} and photometric surveys such as DES \cite{1708.01531,1708.01530,1708.01536}, the Hyper Suprime-Cam \cite{1704.05858,2019PASJ...71...43H,1906.06041} and the Kilo-Degree Survey / VIKING-450 \cite{1902.11265,1812.06077,Joudaki:2019} are approaching completion and the field is preparing for the Stage IV surveys, such as DESI \cite{1611.00036,1907.10688} and LSST \cite{0912.0201,1809.01669} as well as major satellite missions like Euclid \cite{1606.00180} and WFIRST \cite{1904.01174}.

Together with transformational sensitivity increases in the Stage IV surveys, the challenges of understanding and controlling systematic errors are becoming considerably more difficult \cite{1808.07335}. For photometric surveys, the deep surveys sensitive to many more sources inevitably come with crowded fields where effects of blending affect a significant fraction of all sources. The increased blending leads to new uncertainties in isolating sources, measuring their fluxes (required for photometric redshifts) and inferring their shear estimates. These effects in turn lead to subtle sample selection effects, which are amplified by the interaction of the point spread function with blending \cite{1708.01533,1905.01324,1907.10572}. But even with perfect measurements of fluxes, our ability to infer source redshift distributions is hampered by incompleteness in spectroscopic samples used to calibrate redshifts \cite{1903.09325}. Finally, at the depths of Stage IV photometric surveys, instrumental and observational effects, such as scattered light from bright objects, errors in star-galaxy separation, reddening by milky way dust and others will imprint spurious fluctuations on the observed galaxy density field. These fluctuations will, if not correctly accounted for, masquerade as intrinsic large-scale fluctuations in the cosmic density fields.  Therefore, Stage IV photometric experiments are likely to be limited by our ability to control systematics rather than the intrinsic statistical power of the survey.

The community is well aware of these challenges lying ahead. There are two main approaches that are being used in preparation for the arrival of data. On one hand, we are building sophisticated realistic mock data sets, such as LSST DESC Data Challenge 2 \cite{1909.07340,1907.06530}. On the other hand, we are (re-)analyzing existing precursor data to test-drive our methods and codes in a realistic environment. In this paper, we focus on the latter approach using the first data release (DR1) of the Hyper Suprime-Cam Subaru Strategic Program (HSC-SSP) \cite{2018PASJ...70S...8A}. The main advantage of this dataset is its similarity to the LSST data, both in terms of depth and bands as well as primary data reduction and catalog generation. It covers essentially the same bands as LSST, with the exception of missing the UV $u$-band fluxes, which are unlikely to play a major role in cosmological data analysis. We will work with limiting magnitude for 5-$\sigma$ source detection of $i<24.5$, similar to expected magnitude cut to be used for LSST of $i<25.1$ after 1 year \cite{1809.01669}.  The primary data reduction codes used in HSC-SSP and planned for LSST are of the same lineage employing much of the same methods \cite{2018PASJ...70S...5B,1812.03248}. With the exception of a rather small sky area of around 90 square degrees used in this paper, the HSC-SSP data is a perfect example of how the LSST data will look like.

In this paper we focus exclusively on the galaxy clustering part of the data analysis. While the statistically most powerful data combination includes the full 3$\times$2 point analysis (i.e. shear and number density auto and cross-correlations), galaxy clustering along comes with unique challenges, which are the focus of this paper. In particular, galaxy clustering is more sensitive to details of redshift distribution of sources and systematic effects that can generate false fluctuations in number densities. These are the main effects that we study in this paper. We will employ basic tools of the trade, such as measuring power spectrum using mode deprojection and then fit the resulting data taking into account possible deviations from redshift distribution estimates. The question is whether there are sufficient given the statistical precision of the data. We will find that the answer is yes, at least over the total area of HSC-SSP DR1 data.

Due to rather small area, we will be employing simple semi-analytical halo model to make theory predictions. While this model is most certainly not sophisticated enough for the full sky LSST analysis, it suffices for the statistical precision of data at hand. While we will derive some useful constraints on the halo model parameters, the use of halo model here should be viewed as a ``good enough'' substitute for the final modeling, which will likely include bias expansion approaches \cite{0902.0991,1402.5916,1611.09787} and power spectrum emulators \cite{1804.05865,1705.03388}.

This paper is structured as follows. In Section \ref{sec:data}, we describe the HSC-SSP data and how we process it in order to generate a set of galaxy over-density maps together with maps of potential systematics. In Section \ref{sec:methods}, we detail the methodology employed in our analysis and in Section \ref{sec:results}, we present results alongside numerous tests. We discuss and conclude in Section \ref{sec:discussion}.

@@

Finally we use our analysis pipeline described in Sec.~\ref{sec:methods} to investigate the dependence of galaxy clustering on limiting magnitude $m_{\mathrm{lim}}$ of the sample and derive an approximate fitting function for the linear galaxy bias as a function of redshift and $m_{\mathrm{lim}}$.

To this end we split our fiducial galaxy sample into four brighter subsamples with limiting magnitudes $i_{\mathrm{corr}} < 20.5$, $i_{\mathrm{corr}} < 21.5$, $i_{\mathrm{corr}} < 22.5$ and $i_{\mathrm{corr}} < 23.5$, respectively. We then subdivide each of these samples into four redshift bins of approximately equal galaxy number and use our pipeline to compute constraints on HOD parameters for our fiducial analysis variant. This allows us to derive constraints on the large-scale galaxy bias as a function of redshift for each sample. We determine the bias from the mean of the posterior distribution as we find it to yield more stable constraints than the best-fit value. The results for the bias evaluated at the effective redshift of each tomographic bin are shown in Fig.~\ref{fig:magnitude-cuts-bias}, alongside the results for our fiducial sample. As can be seen, we find the linear bias to increase for decreasing limiting magnitude, as expected. Furthermore, the redshift-dependence of the bias can be roughly approximated as inversely proportional to the growth factor, $b(z) \sim \sfrac{1}{D(z)}$, for all samples. In order to obtain a fitting function for the large-scale galaxy bias as a function of redshift and limiting magnitude, we assume it to be separable in $z$ and $m_{\mathrm{lim}}$ and make the following Ansatz:
\begin{equation}
b(z, m_{\mathrm{lim}}) = \bar{b}(m_{\mathrm{lim}}) D(z)^{\alpha}.
\label{eq:bias-fit-func}
\end{equation}  
We determine the values of $\alpha$ and $\bar{b}(m_{\mathrm{lim}})$ in a three-step weighted, linear least squares fit: we first fit Eq.~\ref{eq:bias-fit-func} to all five samples separately and determine our fiducial $\alpha$ as the median of these values\footnote{We note that we find slightly better results using the median, which is the reason for preferring it over the mean.}. We then fit Eq.~\ref{eq:bias-fit-func} to all samples again, obtaining constraints on $\bar{b}(m_{\mathrm{lim}})$ for $\alpha$ fixed to our fiducial value. In a last step, we fit a linear function to $\bar{b}(m_{\mathrm{lim}})$, finally yielding
\begin{align}
\alpha &= -1.32, \\
\bar{b}(m_{\mathrm{lim}}) &= b_{1}m_{\mathrm{lim}} + b_{0},
\label{eq:bias-fit-func}
\end{align}  
where $b_{1} = -0.0627$ and $b_{0} = 2.35$. The results from this fitting function are shown as solid lines in Fig.~\ref{fig:magnitude-cuts-bias}, alongside the values obtained from the HOD fit. As can be seen, the fitting function provides a rather good fit and it might thus become a useful tool for e.g. modeling galaxy bias when forecasting the constraining power of magnitude-limited samples.

\begin{figure}
\begin{center}
\subfigure{\includegraphics[width=0.32\textwidth]{figures/bias-redshift_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_magnitude_cuts_fitting-func.pdf}} 
\subfigure{\includegraphics[width=0.32\textwidth]{figures/bias-growth-redshift_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_magnitude_cuts_fitting-func.pdf}}
\subfigure{\includegraphics[width=0.32\textwidth]{figures/bias-mlim_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_magnitude_cuts_fitting-func.pdf}} 
\caption{Constraints on the large-scale galaxy bias $b(z, m_{\mathrm{lim}})$ as a function of redshift and limiting magnitude for the different galaxy samples considered in this analysis. For all plots, the points denote the values derived from the mean of the posterior distribution of the parameters and the solid lines show the predictions from the fitting function given in Eq.~\ref{eq:bias-fit-func}. The shaded regions denote the $68 \%$ c.l..}
\label{fig:magnitude-cuts-bias}
\end{center}
\end{figure}

@@

This paper has presented a comprehensive analysis of clustering of galaxies from the HSC-SSP DR1 dataset. It has demonstrated that despite relatively small area, the quality of the data allow serious scientific analysis leading to new insights both into physics of galaxy formation as well as methodology of clustering analysis.

In terms of physics we show that a simple flux magnitude cut can be used to create useful samples for galaxy clustering analysis. This contrasts with other approaches that focus on red central galaxies to create smaller samples with more reliable redshift (see e.g. \cite{1507.05460,1807.10163}). Using magnitude cuts yield more galaxies that decrease the shot noise and thus improve the total statistical sensitivity of the survey despite somewhat lower bias leading to less pronounced clustering. In particular, the halo model results in observed galaxies occupying smaller halos toward higher redhifts, but these trends can be well understood by looking at how faint red galaxies drop out from our selection. These results confirm the phenomenological observation that galaxy bias scales approximately inversely with growth function, leading to redshift independent clustering at large redshifts. Our measured evolution of bias is thus consistent with previous measurements, such as those from DEEP2 survey \cite{Coil:2004} and are also in agreement the LSST DESC SRD forecasting exercise, which assumed $b(z) = 0.95/D(z)$ \cite{1809.01669} to better than 5\%. The same data could also be used to compare the effective number densities. In fact \cite{1809.01669} already uses the HSC-SSP data to estimate number densities. We do find, however, that compared to LSST DESC SRD, the area lost to masking is considerably higher, around 20\% rather than 12\% assumed in \cite{1809.01669}.

Encouragingly, we find no barriers to estimating clustering using our samples both in auto and cross-correlation. The deprojection technique has a small but statistically significant effect, especially on large scales.  This bodes well for \ldots

@@

>>>>

In studies of the low redshift universe, surveys of the large scale structure play an increasingly important role. Over a decade ago, the Dark Energy Task Force has divided the evolution of optical experiments into approximate stages \cite{0609591}. The current Stage III experiments, including spectroscopic surveys such as eBOSS \cite{1707.09322,Zhu:2018,1712.08064,1801.02689,1801.02891} and VIPERS \cite{1611.07048,1612.05645,1708.00026} and photometric surveys such as DES \cite{1708.01531,1708.01530,1708.01536}, the Hyper Suprime-Cam \cite{1704.05858,2019PASJ...71...43H,1906.06041} and the Kilo-Degree Survey / VIKING-450 \cite{1902.11265,1812.06077,Joudaki:2019} are approaching completion and the field is preparing for the Stage IV surveys, such as DESI \cite{1611.00036,1907.10688} and LSST \cite{0912.0201,1809.01669} as well as major satellite missions like Euclid \cite{1606.00180} and WFIRST \cite{1904.01174}.

Together with transformational sensitivity increases in the Stage IV surveys, the challenges of understanding and controlling systematic errors are becoming considerably more difficult \cite{1808.07335}. For photometric surveys, the deep surveys sensitive to many more sources inevitably come with crowded fields where effects of blending affect a significant fraction of all sources. The increased blending leads to new uncertainties in isolating sources, measuring their fluxes (required for photometric redshifts) and inferring their shear estimates. These effects in turn lead to subtle sample selection effects, which are amplified by the interaction of the point spread function with blending \cite{1708.01533,1905.01324,1907.10572}. But even with perfect measurements of fluxes, our ability to infer source redshift distributions is hampered by incompleteness in spectroscopic samples used to calibrate redshifts \cite{1903.09325}. Finally, at the depths of Stage IV photometric surveys, instrumental and observational effects, such as scattered light from bright objects, errors in star-galaxy separtation, reddening by milky way dust and others will imprint spurious fluctuations on the observed galaxy density field. These fluctuations will, if not correctly accounted for, masquerade as intrinsic large-scale fluctuations in the cosmic density fields. Therefore, Stage IV photometric experiments are likely to be limited by our ability to control systematics rather than the intrinsic statistical power of the survey.

The community is well aware of these challenges lying ahead. There are two main approaches to preparing for the arrival of data. On one hand, we are building sophisticated, realistic mock data sets, such as LSST DESC Data Challenge 2 \cite{1909.07340,1907.06530}. On the other hand, we are (re-)analyzing existing precursor data to test-drive our methods and codes in a realistic environment. In this paper, we focus on the latter approach and perform an analysis of photometric galaxy clustering using the first data release (DR1) of the Hyper Suprime-Cam Subaru Strategic Program (HSC-SSP) \cite{2018PASJ...70S...8A}. This dataset bears significant similarities to the data expected from LSST, both in terms of survey depth and photometric bands as well as primary data reduction and catalog generation. Specifically, HSC covers essentially the same bands as LSST, with the exception of missing the UV $u$-band fluxes, which are unlikely to play a major role in cosmological data analysis. In this work, we focus on a magnitude-limited galaxy sample with limiting magnitude for 5-$\sigma$ source detection of $i<24.5$, which is similar to the expected magnitude cut to be used for LSST of $i<25.1$ after 1 year \cite{1809.01669}. Finally, the primary data reduction codes used in HSC-SSP and planned for LSST are of the same lineage employing much of the same methods \cite{2018PASJ...70S...5B,1812.03248}. With the exception of a rather small sky area of around 90 square degrees used in this paper, the HSC-SSP data is therefore a perfect proxy for future LSST data.

In this work, we present an analysis of photometric galaxy clustering using HSC DR1 data. We split the data into four tomographic redshift bins and measure both auto- and cross power spectra, correcting for observational systematics using mode deprojection. We then use the halo model coupled with a halo occupation distribution to fit the data and derive constraints on astrophysical parameters, marginalizing over photometric redshift uncertainties. To ensure the stability of our results, we perform a suite of complementary analyses and find our constraints to be robust to photometric redshift uncertainties. We additionally perform extended analyses in which we compute constraints on magnification in our sample and allow for variations in the $\Lambda$CDM cosmological parameters respectively. Finally, we use our data to derive a simple fitting function for the linear galaxy bias as a function of redshift and limiting magnitude of the sample. In our analysis, we make several simplifying approximations; in particular we employ a simple semi-analytical halo model to model the data, which will most certainly not be sophisticated enough for the full sky LSST analysis. However, we find that it suffices for the statistical precision of data at hand, but we view the use of halo model as a ``good enough'' substitute for the final modeling, which will likely include bias expansion approaches \cite{0902.0991,1402.5916,1611.09787} and power spectrum emulators \cite{1804.05865,1705.03388}.

This paper is structured as follows. In Section \ref{sec:data}, we describe the HSC-SSP data and the generation of a set of galaxy over-density maps together with maps of potential systematics. In Section \ref{sec:methods}, we detail the methodology employed in our analysis and in Section \ref{sec:results}, we present results alongside numerous tests. We discuss and conclude in Section \ref{sec:discussion}.
%In this paper we focus exclusively on the galaxy clustering part of the data analysis. While the statistically most powerful data combination includes the full 3$\times$2 point analysis (i.e. shear and number density auto and cross-correlations), galaxy clustering along comes with unique challenges, which are the focus of this paper. In particular, galaxy clustering is more sensitive to details of redshift distribution of sources and systematic effects that can generate false fluctuations in number densities. These are the main effects that we study in this paper. We will employ basic tools of the trade, such as measuring power spectrum using mode deprojection and then fit the resulting data taking into account possible deviations from redshift distribution estimates. The question is whether there are sufficient given the statistical precision of the data. We will find that the answer is yes, at least over the total area of HSC-SSP DR1 data.

@@

Finally we use our analysis pipeline described in Sec.~\ref{sec:methods} to investigate the dependence of galaxy clustering on limiting magnitude $m_{\mathrm{lim}}$ of the sample and derive an approximate fitting function for the linear galaxy bias as a function of redshift and $m_{\mathrm{lim}}$\footnote{We note that we only consider magnitude cuts in the $i$-band and we do not investigate the dependence of our results on the photometric band used to select a magnitude-limited sample.}.

To this end, we split our fiducial galaxy sample into four brighter subsamples with limiting magnitudes $i_{\mathrm{corr}} < 20.5$, $i_{\mathrm{corr}} < 21.5$, $i_{\mathrm{corr}} < 22.5$ and $i_{\mathrm{corr}} < 23.5$, respectively. We then subdivide each of these samples into four redshift bins of approximately equal galaxy number and use our pipeline to compute constraints on HOD parameters for our fiducial analysis variant. We find all subsamples to be well-fit by our fiducial model described in Sec.~\ref{ssec:methods.theory}. In fact, the reduced $\chi^{2}$s for some subsamples are quite low and thus lead to correspondingly high $p$-values, which seem to indicate the presence of overfitting and/or covariance overestimation in our brighter magnitude samples. However, for all subsamples, the distribution of the fit residuals is consistent with a Gaussian and we do not find any significant evidence that our covariance is overestimated by comparing the consistency of power spectra across different HSC fields. We therefore use the results of these HOD fits to derive constraints on the large-scale galaxy bias as a function of redshift for each sample. We determine the bias from the mean of the posterior distribution, as we find it to yield more stable constraints than the best-fit value. The results for the bias evaluated at the effective redshift of each tomographic bin are shown in Fig.~\ref{fig:magnitude-cuts-bias}, alongside the results for our fiducial sample. As can be seen, we find the linear bias to increase for decreasing limiting magnitude, as expected. Furthermore, the redshift-dependence of the bias can be roughly approximated as inversely proportional to the growth factor, $b(z) \sim \sfrac{1}{D(z)}$, for all samples. In order to obtain a fitting function for the large-scale galaxy bias as a function of redshift and limiting magnitude, we assume it to be separable in $z$ and $m_{\mathrm{lim}}$ and make the following Ansatz:
\begin{equation}
b(z, m_{\mathrm{lim}}) = \bar{b}(m_{\mathrm{lim}}) D(z)^{\alpha}.
\label{eq:bias-fit-func}
\end{equation}  
We determine the values of $\alpha$ and $\bar{b}(m_{\mathrm{lim}})$ in a three-step weighted, linear least squares fit: we first fit Eq.~\ref{eq:bias-fit-func} to all five samples separately and determine our fiducial $\alpha$ as the median of these values\footnote{We note that we find slightly better results using the median, which is the reason for preferring it over the mean.}. We then fit Eq.~\ref{eq:bias-fit-func} to all samples again, obtaining constraints on $\bar{b}(m_{\mathrm{lim}})$ for $\alpha$ fixed to our fiducial value. In a last step, we fit a linear function to $\bar{b}(m_{\mathrm{lim}})$, finally yielding
\begin{equation}
\begin{aligned}
\alpha &= -1.32, \\
\bar{b}(m_{\mathrm{lim}}) &= b_{1}m_{\mathrm{lim}} + b_{0},
\label{eq:bias-fit-func-result}
\end{aligned}  
\end{equation}
where $b_{1} = -0.0627$ and $b_{0} = 2.35$. The results from this fitting function are shown as solid lines in Fig.~\ref{fig:magnitude-cuts-bias}, alongside the values obtained from the HOD fit. As can be seen, the fitting function provides a rather good fit and it might thus become a useful tool for e.g. modeling galaxy bias when forecasting the constraining power of magnitude-limited samples.

\begin{figure}
\begin{center}
\subfigure{\includegraphics[width=0.32\textwidth]{figures/bias-redshift_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_magnitude_cuts_fitting-func.pdf}} 
\subfigure{\includegraphics[width=0.32\textwidth]{figures/bias-growth-redshift_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_magnitude_cuts_fitting-func.pdf}}
\subfigure{\includegraphics[width=0.32\textwidth]{figures/bias-mlim_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_magnitude_cuts_fitting-func.pdf}} 
\caption{Constraints on the large-scale galaxy bias $b(z, m_{\mathrm{lim}})$ as a function of redshift and limiting magnitude for the different galaxy samples considered in this analysis. For all plots, the points denote the values derived from the mean of the posterior distribution of the parameters and the solid lines show the predictions from the fitting function given in Equations \ref{eq:bias-fit-func} and \ref{eq:bias-fit-func-result}. The shaded regions denote the $68 \%$ c.l..}
\label{fig:magnitude-cuts-bias}
\end{center}
\end{figure}

@@

In this work, we have presented a comprehensive analysis of photometric galaxy clustering in HSC-SSP DR1 data using a magnitude-limited sample with $i<24.5$. We have split this sample into four tomographic redshift bins and computed all possible auto- and cross power spectra, accounting for observational systematics in number density fluctuations through map-level deprojection. We have then fit the data using a halo model coupled with a halo occupation distribution, marginalizing over a flexible model for photometric redshift uncertainties. Our results are well-fit by our theoretical model including scales up to $k_{\mathrm{max}} = 1$ Mpc$^{-1}$. We find monotonically decreasing average halo masses, which can be interpreted in terms of the drop-out of red galaxies at high redshifts for a flux-limited sample, consistent with previous analyses. In order to test the stability of our results, we performed a suite of alternative analyses, finding our results to be robust to photometric redshift uncertainties. We extended our analysis to include the effects of lensing magnification, which results in a $\sim 3 \sigma$ detection of magnification from our data alone. In addition, we also allowed for variations in the $\Lambda$CDM cosmological parameters, finding that the data are able to constrain $\Omega_{c}$, while $\sigma_{8}$ remains unconstrained. Finally, we used our data to derive a simple fitting function for the linear, large-scale galaxy bias of magnitude-limited samples as a function of redshift and limiting magnitude.

Our analysis hence shows that the quality of the HSC data allows scientific analyses leading to new insights into both physics of galaxy formation as well as methodology of clustering analyses. In terms of physics, we show that a simple magnitude cut can be used to create useful samples for galaxy clustering analyses. This contrasts with other approaches that focus on red central galaxies to create smaller samples with more reliable redshifts (see e.g. \cite{1507.05460,1807.10163}). Using magnitude-limited samples on the other hand, results in larger galaxy samples with smaller shot noise and therefore improved total statistical sensitivity of the survey, despite their less pronounced clustering amplitude due to lower galaxy bias. In addition we find that the cross-correlations between redshift bins carry important information, as they drive the constraints on both parameters accounting for photometric redshift uncertainties as well as lensing magnification amplitude.

Despite the small fraction of sky covered by the data used in this work, HSC DR1 constitutes an ideal proxy for the data expected for LSST. Our analysis demonstrates the feasibility of photometric galaxy clustering analyses using such high signal-to-noise datasets, which bodes well for future analyses using data from LSST.

%Our measured evolution of bias is thus consistent with previous measurements, such as those from DEEP2 survey \cite{Coil:2004} and are also in agreement the LSST DESC SRD forecasting exercise, which assumed $b(z) = 0.95/D(z)$ \cite{1809.01669} to better than 5\%. The same data could also be used to compare the effective number densities. In fact \cite{1809.01669} already uses the HSC-SSP data to estimate number densities. We do find, however, that compared to LSST DESC SRD, the area lost to masking is considerably higher, around 20\% rather than 12\% assumed in \cite{1809.01669}.

@@

The Hyper Suprime-Cam (HSC) collaboration includes the astronomical communities of Japan and Taiwan, and Princeton University. The HSC instrumentation and software were developed by the National Astronomical Observatory of Japan (NAOJ), the Kavli Institute for the Physics and Mathematics of the Universe (Kavli IPMU), the University of Tokyo, the High Energy Accelerator Research Organization (KEK), the Academia Sinica Institute for Astronomy and Astrophysics in Taiwan (ASIAA), and Princeton University. Funding was contributed by the FIRST program from Japanese Cabinet Office, the Ministry of Education, Culture, Sports, Science and Technology (MEXT), the Japan Society for the Promotion of Science (JSPS), Japan Science and Technology Agency (JST), the Toray Science Foundation, NAOJ, Kavli IPMU, KEK, ASIAA, and Princeton University.

This paper makes use of software developed for the Large Synoptic Survey Telescope. We thank the LSST Project for making their code available as free software at  http://dm.lsst.org

This paper is based on data collected at the Subaru Telescope and retrieved from the HSC data archive system, which is operated by Subaru Telescope and Astronomy Data Center at National Astronomical Observatory of Japan. Data analysis was in part carried out with the cooperation of Center for Computational Astrophysics, National Astronomical Observatory of Japan.
